Check Coverage

### 2019-07-01 analysis/coverage_check.Rmd
Update species counts.

@@

check if all bird & mammal biotime data w/id's has an elton match. There are 258 species without a match (38 are birds).
```{r}
biotime_data %>%
  #filter(taxa == "Birds") %>%
  select(id) %>%
  distinct() %>%
  filter(!id %in% elton_bird$id) %>%
  dim()
```

and 605 bird species without an ID, 657 total species
```{r}
biotime_data %>%
  #filter(taxa == "Birds") %>%
  select(id, matchingName) %>%
  distinct() %>%
  filter(is.na(id)) %>%
  dim()
```

Are there any studies for which we have trait data for all species?
```{r}
#join trait and biotime data
bird_data <- biotime_data %>%
  #filter(taxa == "Birds") %>%
  left_join(elton_bird, by = "id",
            na_matches = "never")

>>>>

```{r}
library(tidyverse)
```

@@

check if all bird & mammal biotime data w/id's has an elton match. There are 81 species without a match (67 are birds).
```{r}
no_trait <- biotime_data %>%
  #filter(taxa == "Birds") %>%
  select(id, taxa) %>%
  drop_na(id) %>%
  distinct() %>%
  filter(!id %in% elton_bird$id, !id %in% elton_mamm$id)

dim(no_trait)
```

and 552 species without an ID, some of which are species codes
```{r}
biotime_data %>%
  #filter(taxa == "Birds") %>%
  select(id, matchingName, taxa) %>%
  distinct() %>%
  filter(is.na(id)) %>%
  dim()
```

Are there any studies for which we have trait data for all species?
```{r}
#join trait and biotime data
bird_data <- biotime_data %>%
  filter(taxa == "Birds") %>%
  left_join(elton_bird, by = "id",
            na_matches = "never")
